---
title: "cma440"
author: "chadNoliver"
date: "August 5, 2019"
output: html_document
---

## ISO GIS Market Analysis "Cleaning competition in our area"
##### Upwork ID: https://www.upwork.com/jobs/~0191eb7998b10fd56d



#Accessing the Census API and creating the geoJSON files

#0) Libraries and API Keys

API Key is kept in the `private` subdirectory of this project.  It is ignored by `.git` therefore any clone of this project will need to create a new data subdirectory with their own key saved.

```{r, warning=FALSE, message=FALSE}
#Some are unnecessary - I'll sort out dependencies later

library(magrittr)
library(tidyverse)
library(tidycensus)
library (sf)
library(geojsonio)
library(rgdal)
library(geojsonR)


#options(tigris_use_cache = TRUE)
key <- read.delim(file="private/Census Api Key.txt",header=FALSE)
Sys.setenv(census_api_key=key[[1]])
```



#1) Median Household Income



```{r, warning=FALSE, message=FALSE }


acs.median.hi <- c("B19013_001E")

hi <- st_as_sf(get_acs(geography = "tract",
                       state="OH",
                       variables="B19013_001",
                       geometry=TRUE))

hi <- hi %>%
  group_by(GEOID,NAME) %>% 
  summarize(hi_estimate = round(sum(estimate),2),
            hi_moe = round(moe_sum(moe,estimate=estimate),2)
            )

hi <- hi %>% ungroup()
hi <- hi %>% 

  mutate(
    hi_area=st_area(geometry)* 0.000000386102159,
    hi_estimate_density = round((hi_estimate/hi_area),2),
    hi_moe_density = round((hi_moe/hi_area),2)
  )


n.distinct.hi <- hi %>% 
  summarize(n_distinct(NAME))
```
#2) polygons


##2.1) area code district polygons
Saved as `area.codes`.  Accessed from opendata.arcgis.com.  
```{r}

area.codes <- st_read("https://opendata.arcgis.com/datasets/3d10db43473149f2aa02bb8fd183d2f3_0.geojson")

```




##3 Merge count analysis data with shape files

Define which 
```{r}

library(leaflet)
map <- leaflet() %>% 
  addTiles() %>% 
  addGeoJSON(area.codes)
leaflet(map)
```

##4) Write out geoJSON files
Some need to be filed under a wip directory because the `geojson_write` function and leaflet don't like eachother yet.  Hopefully I can address this later, as this is the most rate-limiting step in the whole process - I've got to manually use mapshaper.org to fix whatever leaflet doesn't like - I can download the mapshaper terminal to fix it but feel that's overkill.  I'll find a solution when I have time.

```{r}
#geojson_write(area.codes, #file="wip-geometry/polygon-nola-zip-pop2.geoJSON", #driver="GeoJSON")

```

